Wide--Field Effects in Redshifted 21~cm Power Spectra

### 2015-03-12 ms.tex
Add preliminary section 5 "Summary"
From aacb3ef:
============

In ms.tex,

(*) Add preliminary section 5 "Summary"
(*) Make minor changes to abstract

Git rename changelot.txt to changelog.txt

Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide--field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide--field measurements imprint a characteristic {\it pitchfork}--shaped signature in this Fourier domain. It is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal. With MWA data sensitivity improved by coherently averaging snapshots aligned in local sidereal time across different observing nights, we confirm the prediction from modeling at $>10\sigma$ level.

@@

>>>>

Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide--field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide--field measurements imprint a characteristic {\it pitchfork}--shaped signature in this Fourier domain. This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal. With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal--noise ratio $>10$.

@@

Fluctuations of redshifted H{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects. This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.

In a recent study, through the use of models for an all--sky foreground and the instrument, the role of wide--field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged. It is referred to as the {\it pitchfork} signature in the delay spectral domain, and is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon. The latter is due to the highly non--linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions. This feature could not be confirmed in individual MWA snapshot observations due to the high level of thermal fluctuations.

By averaging 12 independent snapshots tightly aligned in LST from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the coherency of the observed {\it visibilities}. Foreground power in delay bins near the horizon is distinctly visible with a signal--noise ratio $>10$. In addition, there is a close resemblance in the morphologies of delay power spectra from data and models. Together, they allow us to make a robust confirmation of the nature of wide--field measurements in EoR experiments.
